A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Alternative representations intro

In this last section, some alternative representations of BDDs are discussed
briefly, e.g. BMDs or BEDs. These representations were introduced primarily
because the OBDD representation is insufficient for some problems of practical
relevance. Bryant~\cite{BRYANT95} already reviewed most alternative represenations
but some were introduced after this overview, e.g. the
\textit{Binary Expression Diagrams} introduced by Andersen and
Hulgaard~\cite{ANDERSEN97}. \tbr

>>>>

In this last section, some alternative representations of BDDs are discussed
briefly, i.e. FDDs, ZBDDs and BEDs. These representations were introduced primarily
because the OBDD representation is insufficient for some problems of practical
relevance. Bryant~\cite{BRYANT95} already reviewed most alternative represenations
but some were introduced after this overview, e.g. the
\textit{Binary Expression Diagrams} introduced by Andersen and
Hulgaard~\cite{ANDERSEN97} in 1997.
